Finding and controling biases in dark matter halo concentration estimates

### 2016-07-10 paper/ms.tex
mass-conc intro

We now turn to the question of quantifying the concentration results
of the new algorithm and possible applications of the biases found.

>>>>

We now compare the esults for the mass-concentration
relationship obtained with the three different algorithms.
This helps to compare the concentration results
of the new algorithm and, more importantly, showcase a probable
consequence of the biases detected through bootstrapping.
